---
title: "Philosophy of law cocitations"
output: html_document
date: '2022-03-05'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
```

## Data set acquisition




```{r cars}
source("graph_analysis.R")
```

## Including Plots

## Argumentation (0)

```{r }
tf_idf(0) 
```
```{r}
subgraphCentrality(0) %>% kable() %>% kableExtra::kable_paper()
```

## General jurisprudence (12)

```{r }
tf_idf(12) 
```
```{r}
subgraphCentrality(12) %>% kable() %>% kableExtra::kable_paper()
```

## Punishment and responsibility (11)
```{r }
tf_idf(11) 
```
```{r}
subgraphCentrality(11) %>% kable() %>% kableExtra::kable_paper()
```

## Justice and fairness (9)

```{r }
tf_idf(9) 
```
```{r}
subgraphCentrality(9) %>% kable() %>% kableExtra::kable_paper()
```

## Global justice (2)


```{r }
tf_idf(2) 
```
```{r}
subgraphCentrality(2) %>% kable() %>% kableExtra::kable_paper()
```

## Justice in contracts and torts (7)


```{r }
tf_idf(7) 
```
```{r}
subgraphCentrality(7) %>% kable() %>% kableExtra::kable_paper()
```

## Constitutionalism / legal pluralism / Germans / virtues (5)

```{r }
tf_idf(5) 
```
```{r}
subgraphCentrality(5) %>% kable() %>% kableExtra::kable_paper()
```

## Criminal law (19)

```{r }
tf_idf(19) 
```
```{r}
subgraphCentrality(19) %>% kable() %>% kableExtra::kable_paper()
```

## Law and political theory (6)

```{r }
tf_idf(6) 
```
```{r}
subgraphCentrality(6) %>% kable() %>% kableExtra::kable_paper()
```


## Natural law and non-positivism (8)

```{r }
tf_idf(8) 
```
```{r}
subgraphCentrality(8) %>% kable() %>% kableExtra::kable_paper()
```

## International (criminal) law (1)

```{r }
tf_idf(1) 
```
```{r}
subgraphCentrality(1) %>% kable() %>% kableExtra::kable_paper()
```

## Expert systems (13)

```{r }
tf_idf(13) 
```
```{r}
subgraphCentrality(13) %>% kable() %>% kableExtra::kable_paper()
```

## ? (20)

```{r }
tf_idf(20) 
```
```{r}
subgraphCentrality(20) %>% kable() %>% kableExtra::kable_paper()
```

## Promising and reasonableness (21)

```{r }
tf_idf(21) 
```
```{r}
subgraphCentrality(21) %>% kable() %>% kableExtra::kable_paper()
```

## Classical natural law (23)

```{r }
tf_idf(23) 
```
```{r}
subgraphCentrality(23) %>% kable() %>% kableExtra::kable_paper()
```

## Legal epistemology (3)

```{r }
tf_idf(3) 
```
```{r}
subgraphCentrality(3) %>% kable() %>% kableExtra::kable_paper()
```


## Corporate personhood (18)

```{r }
tf_idf(18) 
```
```{r}
subgraphCentrality(18) %>% kable() %>% kableExtra::kable_paper()
```

## Hate speech (17)

```{r }
tf_idf(17) 
```
```{r}
subgraphCentrality(17) %>% kable() %>% kableExtra::kable_paper()
```

## Kant/Hegel/Kelsen (4)

```{r }
tf_idf(4) 
```
```{r}
subgraphCentrality(4) %>% kable() %>% kableExtra::kable_paper()
```

